#Homework 3

Read in dataset
```{r}
load("hw2_list.rda")
```
Create objects
```{r}
t_df <- bp_list$treatment
p_df <- bp_list$placebo
```


##Task 1

1. Add new status column to both data frames within the bp_list
```{r}
bp_list$treatment$status <- character(20) 
```

```{r}
bp_list$placebo$status <- character(10) 
```

2. Add values to new 'status' columns

```{r}
t_df$status <- ifelse(t_df$post_bp <= 120,"Optimal",
                               ifelse(t_df$post_bp>120 & t_df$post_bp <=130, "Borderline",
                                      ifelse(t_df$post_bp>130, "High",NA)))
```

```{r}
p_df$status <- ifelse(p_df$post_bp <= 120,"Optimal",
                               ifelse(p_df$post_bp>120 & p_df$post_bp <=130, "Borderline",
                                      ifelse(p_df$post_bp>130, "High",NA)))

```

##Task 2

1.Create a function
a. takes in a list with two data frames in it (a treatment and a placebo data frame) as an argument.
```{r}
my_f <- function(list) {
 t_df <- list$treatment
 p_df <- list$placebo
}

```

b. takes in an R function (that would find a summary of a numeric column) with the default value being set to "mean" (notice this is a quoted string).
```{r}
my_f <- function(list) {
 t_df <- list$treatment
 p_df <- list$placebo
if (is.data.frame(t_df))
    t_mean <- colMeans(t_df[, 2:4])
if (is.data.frame(p_df))
    p_mean <- colMeans(p_df[, 2:4])
}
```
 

c. Finds the statistic of interest (as defined by the user input) for the pre, post, and diff columns of both data frames.
– Use my_fun <- get(stat) within the function to get the function from the quoted string.
```{r}
my_f <- function(list) {
 t_df <- list$treatment
 p_df <- list$placebo
{
if (is.data.frame(t_df)) {
    t_mean <- colMeans(t_df[, 2:4])
  }
if (is.data.frame(p_df)) {
    p_mean <- colMeans(p_df[, 2:4])
  }
}
}
```


d. These six values should then be returned as a named list with meaningful names - this is a somewhat challenging part!



e. Finally, apply your function to you list of data frames from previous. Use it without specifying your statistic, 
with specifying your statistic as "var", "sd", "min", and "max".






